He-Man: A domain specific language for lightweight concurrency

### 2012-03-11 paper/paper.tex
Add a note in future work

We also plan to expand the language with the ability to declare functions and
make non-external function calls within a thread. This will make code simpler
and shorter by allowing the programmer to abstract away common functionality
like read and write loops.

In the runtime, our current thread \t{struct}s are larger than necessary.
Because the runtime allocates a \t{struct} on every thread spawn, we should
replace our \t{malloc} calls with calls to a custom slab allocator.

>>>>

XXX: I'm not really sure what we want to put here. I think maybe we
shouldn't have a future work section. If we just want to talk about
the deficencies of the thing we built, that should go somewhere else,
maybe? It isn't really clear we have obvious future research
directions to talk about.

We also plan to expand the language with the ability to declare
functions and make non-external function calls within a thread. This
will make the generated code smaller by allowing the programmer to
abstract away common functionality like read and write loops.

The runtime could be much more carefully tuned.
Because the runtime allocates a \t{struct} on every thread spawn, we should
replace our \t{malloc} calls with calls to a custom slab allocator.
